A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-25 10_applications.tex
redo applications figure

\Cref{applications_overview} shows the widths of generated layer toolpaths for various types of 3D model using the inward distributed beading strategy.
\Cref{application_closeups} highlights closeups of the generated toolpaths.
Thin parts often occur in architectural models, casings, embossed text, gears and microstructures.
Also in larger regions and organic shapes (\cref{applications_case} and \subref{applications_statue}) our method finds succesful application.

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{sources/applications/combined_small_dilated_circled.pdf}
\caption{
Visualization of the widths for the output toolpaths of the inward distributed beading strategy applied to various example application objects.
A legend for the colors can be found in \cref{visualized_accuracy}.
From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a homogeneous lateral thickness tilted gyroid structure and a heterogeneous thickness hexagonal grid.
}
\label{applications_overview}
\end{figure}

\begin{figure*}
\centering
\setlength{\figwidth}{0.1\textwidth}
\setlength{\figheight}{0.1\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/house.png}
\caption{House}\label{applications_house}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/pocket_operator_case.png}
\caption{Case}\label{applications_case}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/david.png}
\caption{Statue}\label{applications_statue}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/tud_logo.png}
\caption{TUD}\label{applications_tud}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/ultimaker_logo.png}
\caption{UM}\label{applications_um}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/pinion_gear_motor.png}
\caption{Gear}\label{applications_gear}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/topopt_bone.png}
\caption{Bone}\label{applications_bone}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/gyroid.png}
\caption{Gyroid}\label{applications_gyroid}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/hex_grid.png}
\caption{Hex}\label{applications_hex}
\end{subfigure}
\caption{
Closeups of results for the inward distributed beading strategy for various applications.
The extrusion widths are visualized exaggeratedly and using a color scheme exaplained in \cref{visualized_accuracy}.
}
\label{application_closeups}
\end{figure*}

>>>>

\Cref{applications_overview} shows the widths of generated layer toolpaths for various types of 3D model using the inward distributed beading strategy.
Thin parts often occur in architectural models, casings, embossed text, gears and microstructures.
Also in larger regions and organic shapes (\cref{applications_case} and \subref{applications_statue}) our method finds succesful application.

@@

\begin{figure*}
\centering
\setlength{\figwidth}{0.099\textwidth}
\setlength{\figheight}{0.099\textwidth}
\begin{subfigure}{\textwidth}\centering
\includegraphics[width=\textwidth]{sources/applications/combined_small_dilated_circled.pdf}
%\caption{Overview}\label{applications_overview}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/house.png}
\caption{House}\label{applications_house}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/pocket_operator_case.png}
\caption{Case}\label{applications_case}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/david.png}
\caption{Statue}\label{applications_statue}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/tud_logo.png}
\caption{TUD}\label{applications_tud}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/ultimaker_logo.png}
\caption{UM}\label{applications_um}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/pinion_gear_motor.png}
\caption{Gear}\label{applications_gear}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/topopt_bone.png}
\caption{Bone}\label{applications_bone}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/gyroid.png}
\caption{Gyroid}\label{applications_gyroid}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/hex_grid.png}
\caption{Hex}\label{applications_hex}
\end{subfigure}
\caption{
Visualization of the widths for the output toolpaths of the inward distributed beading strategy applied to various example application objects.
A legend for the colors can be found in \cref{visualized_accuracy}.
From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a homogeneous lateral thickness tilted gyroid structure and a heterogeneous thickness hexagonal grid.
}
\label{applications_overview}
\end{figure*}
